---
title: "foofactors"
author: "Annie Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to foofactors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is a the [Homework8](http://stat545-ubc.github.io/hw10_package.html) package for [STAT 545](http://stat545-ubc.github.io).

This is built on the demo Jenny posted for students to consult / start with for their homework. There are two functions created by Jenny, `fbind` and `freq_out`. Two new functions that are created by Annie Li, `is_char` and `fac`, have been added to the package. 

Here's how to use the `foofactors` package.

```{r}
#install_github("AnnieXuanLi/foofactors")
library(foofactors)
```

## `fbind` 
### Description
Create a new factor from two existing factors, where the new factor's levels are the union of the levels of the input factors.

### Examples
```{r}
fbind(iris$Species[c(1, 51, 101)], PlantGrowth$group[c(1, 11, 21)])
fbind(factor(c(1,3,5)), factor(c(2,4,6)))
fbind(factor(c("a","b","c")), factor(c("d","f","e")))
```

## `freq_out`
### Description
Make a frequency table for a factor

### Examples
```{r}
freq_out(iris$Species)
```

## `is_char`
### Description
Detect factors that should be character because # unique values = length

### Examples
```{r}
is_char(factor(c("a", "b", "c", "d")))
is_char(factor(c(1, 3, 5, 4, 1, 6)))
```

## `fac`
### Description
Turn a vector to a factor and set levels to the order in which they appear in the data

### Examples
```{r}
fac(c("a", "c", "b", "e"))
fac(c(3, 2, 5, 1, 1, 1, 6))
fac(c("a", "c", "d", "b", "b", "c"))
```



